---
title: "R for Art Sundays"
date: "2019-04-28"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
```

# Drawing 10 Million Points With ggplot: Clifford Attractors

by [Antonio Sánchez Chinchón](https://twitter.com/aschinchon)

An R experiment to create images generated by the trajectory of a particle according to Clifford attractors.

Made with `Rcpp`, `tidyverse`


**Blog post explaining the experiment:** [Drawing 10 Million Points With ggplot: Clifford Attractors](https://fronkonstin.com/2017/11/07/drawing-10-million-points-with-ggplot-clifford-attractors/)

**Inspired by:** [Clifford Attractors, by Paul Bourke](http://paulbourke.net/fractals/clifford/)


```{r code, message=FALSE, warning=FALSE, error=FALSE, fig.width=8, fig.height=8, dpi=600}

library(Rcpp)
library(tidyverse)

opt <-  theme(legend.position  = "none",
              panel.background = element_rect(fill="black"),
              plot.background  = element_rect(fill="black"),
              axis.ticks       = element_blank(),
              panel.grid       = element_blank(),
              axis.title       = element_blank(),
              axis.text        = element_blank())


cppFunction('DataFrame createTrajectory(int n, double x0, double y0, 
            double a, double b, double c, double d) {
            // create the columns
            NumericVector x(n);
            NumericVector y(n);
            x[0]=x0;
            y[0]=y0;
            for(int i = 1; i < n; ++i) {
            x[i] = sin(a*y[i-1])+c*cos(a*x[i-1]);
            y[i] = sin(b*x[i-1])+d*cos(b*y[i-1]);
            }
            // return a new data frame
            return DataFrame::create(_["x"]= x, _["y"]= y);
            }
            ')

a <- -1.7729
b <- 1.5791
c <- 1.4839
d <- 1.1109

df <- createTrajectory(10000000, 0, 0, a, b, c, d)

plot <- ggplot(df, aes(x, y)) + 
  geom_point(color="white", shape=46, alpha=.01) + 
  opt

plot

```



-----


```{r, results='asis', echo=FALSE}

cat(
  " Compiled: ",
  as.character(Sys.Date()),
  sep = ""
)
```
